\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\pagecolor{white}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\graphicspath{ {./images/} }   
\begin{document}

\title{Enhancing Path Efficiency: Innovations in the Artificial Feeding Birds Algorithm for Solving TSP Problems\\
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}

\input{./tsp.tex}
\input{./algorithm_foundation.tex}
\input{./methodology.tex}
\input{./improvements.tex}
\input{./analysis.tex}


\section*{References}

\begin{thebibliography}{00}
\bibitem{lin} Lin, S. (1965), Computer Solutions of the Traveling Salesman Problem. Bell System Technical Journal, 44: 2245-2269. https://doi.org/10.1002/j.1538-7305.1965.tb04146.x
\bibitem{afb} Jean-Baptiste Lamy. Artificial Feeding Birds (AFB): a new metaheuristic inspired by the behavior of pigeons. Advances in nature-inspired computing and applications, 2019, 10.1007/978-3-319-96451- 5\_3 . hal-02264232
\bibitem{3_opt} Jingyan Sui, Shizhe Ding, Ruizhi Liu, Liming Xu, Dongbo Bu Proceedings of The 13th Asian Conference on Machine Learning, PMLR 157:1301-1316, 2021.

\end{thebibliography}
\vspace{12pt}

\end{document}
